$K$-corrections and filter transformations \\ from the restframe ultraviolet to the near infrared

### 2006-06-07 docs/paper/kcorrect_figures.tex
add
git-svn-id: svn+ssh://howdy.physics.nyu.edu/usr/local/svn/kcorrect/trunk@553 75dff457-8751-0410-ab1a-cd701654ce6b

>>>>

\clearpage
\stepcounter{thefigs}
\begin{figure}
\figurenum{\fignum}
\plotone{lemma.eps}
\caption{\label{lemma} Example diagram of definition of $\phi$ in the
	text. $\chi^2$ represents the actual $\chi^2$ while $\phi$ is
	designed such that it exceeds $\chi^2$ except at the single point
	$W$. By minimizing $\phi$ we can find a point $W^\ast$ that we know
	to have an equal or better $\chi^2$ than that at $W$. }
\end{figure}
